%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Deedy - One Page Two Column Resume
% LaTeX Template
% Version 1.2 (16/9/2014)
%
% Original author:
% Debarghya Das (http://debarghyadas.com)
%
% Original repository:
% https://github.com/deedydas/Deedy-Resume
%
% IMPORTANT: THIS TEMPLATE NEEDS TO BE COMPILED WITH XeLaTeX
%
% This template uses several fonts not included with Windows/Linux by
% default. If you get compilation errors saying a font is missing, find the line
% on which the font is used and either change it to a font included with your
% operating system or comment the line out to use the default font.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% 
% TODO:
% 1. Integrate biber/bibtex for article citation under publications.
% 2. Figure out a smoother way for the document to flow onto the next page.
% 3. Add styling information for a "Projects/Hacks" section.
% 4. Add location/address information
% 5. Merge OpenFont and MacFonts as a single sty with options.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% CHANGELOG:
% v1.1:
% 1. Fixed several compilation bugs with \renewcommand
% 2. Got Open-source fonts (Windows/Linux support)
% 3. Added Last Updated
% 4. Move Title styling into .sty
% 5. Commented .sty file.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Known Issues:
% 1. Overflows onto second page if any column's contents are more than the
% vertical limit
% 2. Hacky space on the first bullet point on the second column.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\documentclass[]{deedy-resume-openfont}
\usepackage{fancyhdr}
\geometry{left=1.0cm,right=1.0cm,top=0.55cm,bottom=0.45cm}
 
\pagestyle{fancy}
\fancyhf{}
 
\begin{document}

\renewcommand{\sectionsep}{\vspace{3pt}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\namesection{Mikołaj Mieszko}{Charchuta}{ \urlstyle{same}\href{https://www.github.com/mmcharchuta}{github.com/mmcharchuta}| \href{https://www.linkedin.com/in/mmcharchuta/}{linkedin.com/in/mmcharchuta/}\\ | +48 730 359 228 | \href{mailto:mmcharchuta@gmail.com}{mmcharchuta@gmail.com} | Poznań, Poland (open to remote, hybrid, relocation)
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.33\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Education} 

\subsection{AMU, Poznan}
\descript{MSc in Bioinformatics}
\location{Oct 2025 -- Jul 2027}
{\footnotesize Thesis: \textit{In silico analysis of Cry9 toxins and their genetic determinants in the Bacillus thuringiensis pangenome} (first-author article in preparation).}\\
\sectionsep

\subsection{AMU, Poznan}
\descript{BSc in Bioinformatics \& Biotechnology}
\location{Oct 2021 -- Sep 2025}
{\footnotesize Thesis: \textit{Comparison of naïve methods for taxonomic classification of microorganisms using marker gene sequences} (created the \href{https://github.com/mmcharchuta/NaiveR}{NaïveR R package}).}\\
\sectionsep

\subsection{Charles University, Prague}
\descript{Erasmus+ Exchange}
\location{Winter 2022/23, Summer 2023/24}
{\footnotesize \textbullet{} Institute of Microbiology, Czech Academy of Sciences: \textit{Profiling metabolism of complex microbial communities with Stable Isotope Probing and meta-omics}.\\
\textbullet{} Faculty of Natural Sciences, Charles University: Applying CryoEM for studying the structures of cultivated meat proteins.}\\
\sectionsep

\subsection{University of Gdansk}
\descript{National Exchange}
\location{Winter semester 2023/24}
{\footnotesize \textbullet{} Faculty of Biotechnology, UoG \& Gdansk Medical University: Metabolomics \& proteomics of SynComs bioprotective against plant pathogens.\\
\textbullet{} Faculty of Biology, UoG: Genomes of phages infecting uropathogenic \textit{E. coli}.}\\

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Skills}
\subsection{Programming}
R \textbullet{} Bash \textbullet{} Python \textbullet{} C++ \\
Git \textbullet{} Docker \textbullet{} AWS \textbullet{} Slurm \textbullet{} Nextflow
\sectionsep

\subsection{Bioinformatics}
Transcriptomics (DESeq2, rMATS) \\
Genomics (samtools, GATK, Hi-C/3C-seq) \\
Metagenomics (QIIME2, mothur, NaïveR)
\sectionsep

\subsection{Thesis Skills}
R package development (NaïveR) \\
Taxonomic classification benchmarking \\
Pangenome analysis \textbullet{} Cry toxin gene mining
\sectionsep

\subsection{Languages}
English (C2) \textbullet{} Polish (Native) \textbullet{} German (B2)
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage} 
\hfill
\begin{minipage}[t]{0.66\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Experience}
\runsubsection{AMU Microbiology Dept.}
\descript{| Bioinformatician}
\location{Sep 2025 -- Present, 20\% FTE | Poznań, PL}
\begin{tightemize}
\item Genomics of pests and biopesticidal microbes; predictive protein design.
\item Hi-C/3C-seq analysis and workflow development.
\end{tightemize}
\sectionsep

\runsubsection{Bene Meat Technologies}
\descript{| Bioinformatician}
\location{Mar 2024 -- Jul 2024 | Prague, CZ}
\begin{tightemize}
\item Transcriptomics and nanopore sequencing support.
\item Bioreactor automation and production bioinformatics support.
\end{tightemize}
\sectionsep

\runsubsection{Leiden University Medical Center}
\descript{| Intern, Endocrinology Dept.}
\location{Jun 2023 -- Oct 2023 | Leiden, NL}
\begin{tightemize}
\item Bioinformatics support, data visualization, and pipeline creation.
\item Co-authored publication in AJP (murine model work).
\end{tightemize}
\sectionsep

\runsubsection{MNM Diagnostics}
\descript{| Genome Analyst}
\location{Feb 2022 -- Jul 2022 | Poznań, PL}
\begin{tightemize}
\item Automation, WGBS (epigenomics)  ML feature extraction, data-lake.
\item Genome analysis interpretation. Cooperation with clinicians.

\end{tightemize}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     PROJECTS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Projects}
\runsubsection{Testing DynaMAP\texttrademark{} -- Optical Mapping \& Nanopore}
\descript{| Bachelor Thesis Project (Team Lead)}
\location{Oct 2023 -- Oct 2025}
\begin{tightemize}
\item Student research grant; led team benchmarking microbiome profiling methods.
\item Coordinated with Perseus Biomics - a startup specializing in rapid diagnostics - to test their DynaMAP\texttrademark{} technology for microbiome profiling, comparing it against established methods like 16S rRNA sequencing and shotgun metagenomics.
\end{tightemize}
\sectionsep

\runsubsection{SPUN -- Illumina Sequencing}
\descript{| International Grant}
\location{Nov 2022 -- Apr 2024}
\begin{tightemize}
\item Predicted global biodiversity hotspots with ML.
\item Field research video: \href{https://youtu.be/6frg_7ykXvc?t=128}{\url{https://youtu.be/6frg_7ykXvc?t=128}}.
\end{tightemize}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     PUBLICATIONS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Publications}
{\footnotesize
\textbf{In silico analysis of Cry9 toxins and their genetic determinants in the Bacillus thuringiensis pangenome}\\
In preparation (expected 2026). Charchuta, M. M. (first), Baranek, J. (second), et al.\\
\textbf{Combination of dietary fiber and exercise training improves fat loss in mice but does not ameliorate MASLD more than exercise alone}\\
American Journal of Physiology-Gastrointestinal and Liver Physiology, 2025. Kovynev, A.; Charchuta, M. M.; et al.\\
\textbf{WED-517 Oatmeal a day does not keep the doctor away: inulin and exercise impact on MASLD amelioration and gut-liver crosstalk}\\
Journal of Hepatology, 2024. Kovynev, A.; Charchuta, M.; et al.
}

\end{minipage}

\vspace*{\fill}
\noindent{\tiny I consent to the use of my personal data for recruitment purposes, in line with the GDPR (EU) 2016/679. My information will be stored and processed solely for the duration of the hiring process.}

\end{document}
